### 2023-06-30 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on paper

\begin{comment}
%\begin{figure}[h]
\begin{figure*}[b]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
  \caption{\label{fig:RA6} \small A vesicle passing through a stenosed
  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
  dimensionless maximum velocity is $U = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=1$; (b) single-component with
  bending modulus $b=0.55$; (c) multicomponent.}
%\end{figure}
\end{figure*}
\end{comment}

We consider a vesicle with reduced area $\alpha = 0.6$ passing through a
closely-fitting channel, with a dimensionless maximum velocity of $U =
0.25$. Figure~\ref{fig:RA6} shows six time steps of a single-component
vesicle with bending stiffness (a) $b=1$ and (b) $b=0.55$, and a
multicomponent vesicle with an initially random distribution of lipids
(c). In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region. We
consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
reduced area $\alpha = 0.4$. The main difference between the two reduced
areas is that the vesicles with smaller reduced area undergo
tank-treading motions. As mentioned earlier, tank treading occurs when
the top and bottom lubrication layers differ in size. The size of the
lubrication layers in all six cases are in Figure~\ref{fig:lubrication}.

\begin{comment}
%\begin{figure}[h]
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
  \caption{\label{fig:RA4} \small A vesicle passing through a stenosed
  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
  dimensionless maximum velocity is $U = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=1$; (b) single-component with
  bending modulus $b=0.55$; (c) multicomponent. The multicomponent
  vesicle travels slightly faster, so it leaves the stenosed region
  earlier than the single-component cases (see
  Figure~\ref{fig:vesVelocity}).}
%\end{figure}
\end{figure*}
\end{comment}

@@

\begin{figure}[h]
    \centering
    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
    \caption{\label{fig:lubrication} \small The size of the lubrication
    layer of a stiff single component (red), floppy single component
    (green), and multicomponent (blue) vesicle passing through stenosis.
    Solid lines are the layer thickness between the vesicle and the top
    wall, and dashed lines are the layer thickness between the vesicle
    and the bottom wall. The reduced area of the vesicles are (a)
    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
\end{figure}

The tank-treading velocities of the examples with reduced area $\alpha = 0.4$ are in Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the dashed black lines are also included, and the four marker points are the Lagrangian points where the tangential velocities are computed. For reduced area $\alpha = 0.4$, the single-component ($b=1$) and multicomponent vesicles are clearly tank treading. Since the single-component case has a larger difference between its top and bottom boundary layers, it tank treads faster than the multicomponent case. In addition, since the top boundary layer is larger in both cases, they both tank-tread in the same direction---counterclockwise. In contrast, the single-component vesicle with $b=0.55$ tank-treads in the clockwise direction; note, however, that this example is still undergoing some deformations, so a constant tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle undergoes deformations while in the stenosed geometry and a constant tank-treading velocity is not observed, so a plot is not included.

@@

%\begin{figure}[h]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
%    \end{minipage}
%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
%    \label{fig:tankTreadRAp4}}
%\end{figure}
\begin{figure*}[t]
%\begin{figure}[htp]
  \centering
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{(a)}{figures/TankTreadingFigs_composite_SC.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{(b)}{figures/TankTreadingFigs_composite_SCp55.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{(c)}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:tankTreadRAp4} \small The tangential velocity at
  four Lagrangian points on a (a) single-component vesicle with $b = 1$
  (b) single-component vesicle with $b = 0.55$, and (c) multicomponent
  vesicle. The reduced area is $\alpha = 0.4$ in all cases. Also
  illusrated is the vesicle shape and the four Lagrangian points at the
  location indicated by the dash line.}
%\end{figure}
\end{figure*}

@@

While the size of the lubrication layers affect the tank-treading
behavior and the excess pressure, it has almost no effect on the
migration speed of the vesicle. In Figure~\ref{fig:vesVelocity}, we plot
the average velocity of the vesicle as it passes through the stenosed
region. With the exception of the single-component vesicle with $b=1$
and $\alpha = 0.6$, the average vesicle speed is constant. Obviously,
this average velocity would be affected by the maximum imposed velocity,
$U$.

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/Fig9.pdf}
    %\input{figures/Fig9.tikz}
    \caption{\label{fig:vesVelocity} \small The average vesicle velocity as it passes through the stenosed region. The vesicle stiffness and reduced area have no significant effect.}
\end{figure}

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the soild wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall.

Using the definition of the lubrcication layer outlined in
Section~\ref{sec:LL} fit the horizontal flow profile to a quadratic
function and plot the coefficients of the Poisseuille and linear shear
in Figure~\ref{}. We only consider cases where the vesicle has reached a
steady shape is only under going tank treading. We observe that the
Poisseuille coefficient can be either positive or negative, meaning that
the pressure in the lubcrication layer switches signs. This behavior is
caused when the tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
where
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the variational derivative of the membrane energy with respect to the
lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
=\sigma_s$ which is the usual Marangoni effect.

>>>>

%\begin{comment}
%\begin{figure}[h]
\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
  \caption{\label{fig:RA6} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=1$; (b) single-component with
  bending modulus $b=0.55$; (c) multicomponent.}
%\end{figure}
\end{figure*}
%\end{comment}

We consider a vesicle with reduced area $\alpha = 0.6$ passing through a
closely-fitting channel (stenosis), with a capillary number $Ca = 0.25$.
Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle
with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a multicomponent
vesicle with an initially random distribution of lipids. In all plots,
the color is the dimensionless bending modulus of the multicomponent
vesicle that remains bounded in $[0.1,1]$ by using the new bending
modulus~\eqref{eqn:tanhBending}. A single Lagrangian point is included
to visualize tank-treading behavior. There are slight differences
between the three cases, with the most noticeable being that the
multicomponent vesicle has higher curvature in the floppy region. We
consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
reduced area $\alpha = 0.4$. The main difference between the two reduced
areas is that the vesicles with smaller reduced area undergo
tank-treading motions. As mentioned earlier, tank treading occurs when
the top and bottom lubrication layers differ in size. The size of the
lubrication layers in all six cases are in Figure~\ref{fig:lubrication}.

%\begin{comment}
%\begin{figure}[h]
\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
  \caption{\label{fig:RA4} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a) single-component
  with bending modulus $b=1$; (b) single-component with bending modulus
  $b=0.55$; (c) multicomponent.}
%  The multicomponent vesicle travels
%  slightly faster, so it leaves the stenosed region earlier than the
%  single-component cases (see Figure~\ref{fig:vesVelocity}).}
%\end{figure}
\end{figure*}
%\end{comment}

@@

\begin{figure}[h]
    \centering
    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
    \caption{\label{fig:lubrication} \small The size of the lubrication
    layer of a stiff single-component (red), floppy single-component
    (green), and multicomponent (blue) vesicle passing through stenosis.
    Solid lines are the layer thickness between the vesicle and the top
    wall, and dashed lines are the layer thickness between the vesicle
    and the bottom wall. The reduced area of the vesicles are (a)
    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
\end{figure}

The tank-treading velocities of the examples with reduced area $\alpha =
0.4$ are in Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the
dashed black lines are also included, and the four marker points are the
Lagrangian points where the tangential velocities are computed. For
reduced area $\alpha = 0.4$, the single-component ($b=1$) and
multicomponent vesicles are clearly tank treading. Since the
single-component case has a larger difference between its top and bottom
boundary layers (see Figure~\ref{fig:lubrication)}, it tank treads
faster than the multicomponent case. In addition, since the top boundary
layer is larger in both cases, they both tank-tread in the same
direction---counterclockwise. In contrast, the single-component vesicle
with $b=0.55$ tank-treads in the clockwise direction; note, however,
that this example is still undergoing some deformations, so a constant
tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle
undergoes deformations while in the stenosis, and a constant
tank-treading velocity is not observed

@@

%\begin{figure}[h]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
%    \end{minipage}
%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
%    \label{fig:tankTreadRAp4}}
%\end{figure}
\begin{figure*}[t]
%\begin{figure}[htp]
  \centering
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{(a)}{figures/TankTreadingFigs_composite_SC.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{(b)}{figures/TankTreadingFigs_composite_SCp55.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{(c)}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:tankTreadRAp4} \small The tangential velocity at
  four Lagrangian points on a (a) single-component vesicle with $b = 1$
  (b) single-component vesicle with $b = 0.55$, and (c) multicomponent
  vesicle. The reduced area is $\alpha = 0.4$ in all cases. Also
  illustrated is the vesicle shape and the four Lagrangian points at the
  location indicated by the dash line.}
%\end{figure}
\end{figure*}

@@

While the size of the lubrication layers affect the tank-treading
behavior and the excess pressure, it has almost no effect on the
migration speed of the vesicle. 
%In Figure~\ref{fig:vesVelocity}, we plot
%the average velocity of the vesicle as it passes through the stenosed
%region.
With the exception of the single-component vesicle with $b=1$ and
$\alpha = 0.6$, which has an average vesicle speed about 5\% slower, the
average vesicle speed is constant. Obviously, this average velocity
would be affected by the capillary number, $Ca$.

%\begin{figure}[H]
%  \centering
%  \includegraphics[width=\columnwidth]{figures/Fig9.pdf}
%%  \input{figures/Fig9.tikz}
%  \caption{\label{fig:vesVelocity} \small The average vesicle velocity
%  as it passes through stenosis. The vesicle stiffness and reduced area
%  have no significant effect.}
%\end{figure}

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient can be either positive or negative, meaning
that the pressure in the lubrication layer switches signs. This behavior
is caused when the tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
where
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the variational derivative of the membrane energy with respect to the
lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
=\sigma_s$ which is the usual Marangoni effect.
